House Price in Nanjing: Exploring Distribution of House Price and Performing Prediction with Multiple Linear Regression and Random Forest

### 2023-12-01 output/paper/paper.qmd
Change title

---
title: "House Price in Nanjing: Comparing Multiple Linear Regression and Random Forest"
author: "Yufei Liu"
thanks: "Code and data are available at: https://github.com/Florence-Liu/house-price"
date: today
date-format: long
abstract: "House price in Nanjing has grown rapidly and became a concern in recent years. This paper examines the relationship between house price in Nanjing, structural attributes of the property, and location using open data collected from Lianjia.com, and predict house price in Nanjing with different models. We find a geographically-imbalanced distribution of house price in Nanjing with large variance within and between each district. By comparing the MAE and RMSE, we find the random forest model gives a better prediction accuracy than the multiple linear regression model. Further work could include geocoding data to perform spatial autocorrelation analysis that consider the spatial effect in the data. "
format: pdf
number-sections: true
toc: false
bibliography: references.bib
---

>>>>

---
title: "House Price in Nanjing: Exploring Distribution of House Price and Performing Prediction with Multiple Linear Regression and Random Forest"
author: "Yufei Liu"
thanks: "Code and data are available at: https://github.com/Florence-Liu/house-price"
date: today
date-format: long
abstract: "House price in Nanjing has grown rapidly and became a concern in recent years. This paper examines the relationship between house price in Nanjing, structural attributes of the property, and location using open data collected from Lianjia.com, and predict house price in Nanjing with different models. We find a geographically-imbalanced distribution of house price in Nanjing with large variance within and between each district. By comparing the MAE and RMSE, we find the random forest model gives a better prediction accuracy than the multiple linear regression model. Further work could include geocoding data to perform spatial autocorrelation analysis that consider the spatial effect in the data. "
format: pdf
number-sections: true
toc: false
bibliography: references.bib
---
